Mean and variance functions used to simulate Gaussian data

### 2018-12-04 analysis/gaussian_signals.Rmd
wflow_publish("gaussian_signals.Rmd")

```{r plot-mean-functions, fig.height=10, fig.width=6}
plot_grid(qplot(t,mu.sp,  geom = "line",xlab = "",ylab = "",main = "Spikes"),
          qplot(t,mu.bump,geom = "line",xlab = "",ylab = "",main = "Bumps"),
          qplot(t,mu.blk, geom = "line",xlab = "",ylab = "",main = "Blocks"),
          qplot(t,mu.ang, geom = "line",xlab = "",ylab = "",main = "Angles"),
          qplot(t,mu.dop, geom = "line",xlab = "",ylab = "",main = "Doppler"),
          qplot(t,mu.blip,geom = "line",xlab = "",ylab = "",main = "Blip"),
          qplot(t,mu.cor, geom = "line",xlab = "",ylab = "",main = "Corner"),
		  nrow = 4,ncol = 2)
```

@@

These are rescaled in the simulations to achieve the desired signal
to noise ratios.

>>>>

```{r plot-mean-functions, fig.height=10, fig.width=6}
plot_grid(qplot(t,mu.sp,  geom="line",xlab="",ylab="",main="Spikes (sp)"),
          qplot(t,mu.bump,geom="line",xlab="",ylab="",main="Bumps (bump)"),
          qplot(t,mu.blk, geom="line",xlab="",ylab="",main="Blocks (blk)"),
          qplot(t,mu.ang, geom="line",xlab="",ylab="",main="Angles (ang)"),
          qplot(t,mu.dop, geom="line",xlab="",ylab="",main="Doppler (dop)"),
          qplot(t,mu.blip,geom="line",xlab="",ylab="",main="Blip (blip)"),
          qplot(t,mu.cor, geom="line",xlab="",ylab="",main="Corner (cor)"),
		  nrow = 4,ncol = 2)
```

@@

These are rescaled in the simulations to achieve the desired
signal-to-noise ratios (see the paper for a more detailed
explanation).
